COG-ED Manuscript

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
finished results reporting for 3b

## Hypothesis 3b: NASA-TLX scores negatively predict individual NFC scores.

Intercept:
`r apa_print(hypothesis3b)$estimate$Intercept`

Predictor $AxAUC$:
`r apa_print(hypothesis3b)$estimate$h3_data_axauc`

Predictor $AUC$ NASA-TLX:
`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`

Fit:
`r apa_print(hypothesis3b)$estimate$modelfit$r2`

Effect size and confidence interval:

$\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,2]`

Bayes factors:

$BF10=$ `r extractBF(hypothesis3b_BF)$bf[1]` for predictor $AxAUC$

$BF10=$ `r extractBF(hypothesis3b_BF)$bf[2]` for predictor $AUC$ NASA-TLX

>>>>

## Hypothesis 3b: Participants with high NFC scores have lower NASA-TLX scores in every n-back level than participants with low NFC scores.

Main effect of the NFC group:

`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, §BF10=$ `r format(extractBF(hypothesis3b_BF["nfcmedian"])$bf, digits = 2)`

Main effect of the n-back level:

`r apa_print(hypothesis3b_model)$full_result$level`, §BF10=$ `r format(extractBF(hypothesis3b_BF["level"])$bf, digits = 2)`

Interaction effect of NFC group and n-back level:

`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`, §BF10=$ `r format(extractBF(hypothesis3b_BF["level + nfcmedian"])$bf, digits = 2)`

Paired contrasts for the main effect of n-back level:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3b_rmanova,
  caption = "Main effects and interaction of NFC group and n-back level on NASA-TLX scores",
  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```
